Data Preparation

### 2019-03-11 Data Preparation.Rmd
debug incoherence between data preparation and pillar 1

  # Select: Student ID, course ID, when course taken and grade 
  select(
    `Student ID`   = `Student Number`,
    `Course ID`    = `Module (Abbrev.)`,
    Year_numerical =`Academic Year`,
    Period         = `Academic Session`,
    Grade          = `Grade symbol`
  )
```

@@

  select(
    - Year_numerical,
    - Period
    )
```

>>>>

  # Select: Student ID, course ID, when course taken and grade 
  select(
    `Student ID`   = `Student Number`,
    `Course ID`    = `Module (Abbrev.)`,
    Year_numerical = `Academic Year`,
    Period         = `Academic Session`,
    Grade          = `Grade symbol`
  )
```

@@

  )
```
